Parallel multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-12-13 hpmoon-coor.tex
Explained why NSGA2. Closes #5

In this paper we analyse several coevolutionary algorithms we have implemented by using a parallel multi-objective baseline algorithm (B) as a framework. Here, we have used the NSGA-II algorithm as the baseline algorithm. The population is distributed among $P$ islands. After a fixed number of generations, one individual in a given island is migrated to another random island, thus avoiding to synchronize the global Pareto Front (PF) every certain number of generations as other methods described in Section 2 do. At the end of the run, the Pareto Fronts of all islands are aggregated into a new one, and the quality measures are evaluated.
Different coevolutionary alternatives can be devised to evolve the subpopulations according to the decision space to be explored by each islands. Here we will consider three methods in which each island only performs crossover and mutation in specific sections of the individuals.

@@

Also, more distributed implementations in several systems (such as a
GPUs or heterogeneous clusters) with different amounts of
islands/processors, will be used to perform a scalability study of the
different methods, being the transmission time between islands a
relevant issue to address. Finally, new benchmarks and real problems
will also be  used to validate this approach.

@@

%\bibliographystyle{elsarticle-num}

%\bibliography{hpmoon-eswa}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Alba13parallel}
E.~Alba, G.~Luque, S.~Nesmachnow, Parallel metaheuristics: recent advances and
  new trends, International Transactions in Operational Research 20~(1) (2013)
  1--48.
\newblock \href {http://dx.doi.org/10.1111/j.1475-3995.2012.00862.x}
  {\path{doi:10.1111/j.1475-3995.2012.00862.x}}.

\bibitem{Folino03cellular}
G.~Folino, C.~Pizzuti, G.~Spezzano, A scalable cellular implementation of
  parallel genetic programming, {IEEE} Trans. Evolutionary Computation 7~(1)
  (2003) 37--53.

\bibitem{Alba02Parallelism}
E.~Alba, M.~Tomassini, Parallelism and evolutionary algorithms, {IEEE} Trans.
  Evolutionary Computation 6~(5) (2002) 443--462.

\bibitem{Luna15Survey}
F.~Luna, E.~Alba, Parallel multiobjective evolutionary algorithms, in:
  J.~Kacprzyk, W.~Pedrycz (Eds.), Springer Handbook of Computational
  Intelligence, Springer, 2015, pp. 1017--1031.

\bibitem{Branke04Parallelizingcone}
J.~Branke, H.~Schmeck, K.~Deb, R.~S. Maheshwar, Parallelizing multi-objective
  evolutionary algorithms: cone separation, in: Proceedings of the {IEEE}
  Congress on Evolutionary Computation, {CEC} 2004, 19-23 June 2004, Portland,
  OR, {USA}, {IEEE}, 2004, pp. 1952--1957.

\bibitem{Mukhopadhyay14Survey}
A.~Mukhopadhyay, U.~Maulik, S.~Bandyopadhyay, C.~A.~C. Coello, A survey of
  multiobjective evolutionary algorithms for data mining: Part {I}, {IEEE}
  Trans. Evolutionary Computation 18~(1) (2014) 4--19.

\bibitem{Chavez15MO}
F.~C. de~la O, E.~Clemente, D.~E. Hern{\'{a}}ndez, F.~F. de~Vega, G.~Olague, A
  multi-objective evolutionary algorithm for interaction systems based on laser
  pointers, in: A.~M. Mora, G.~Squillero (Eds.), Applications of Evolutionary
  Computation - 18th European Conference, EvoApplications 2015, Copenhagen,
  Denmark, April 8-10, 2015, Proceedings, Vol. 9028 of Lecture Notes in
  Computer Science, Springer, 2015, pp. 504--516.
\newblock \href {http://dx.doi.org/10.1007/978-3-319-16549-3}
  {\path{doi:10.1007/978-3-319-16549-3}}.

\bibitem{Hidalgo16residualstress}
J.~I. Hidalgo, R.~Fern{\'{a}}ndez, J.~M. Colmenar, F.~Cioffi, J.~L.
  Risco{-}Mart{\'{\i}}n, G.~Gonz{\'{a}}lez{-}Doncel, Using evolutionary
  algorithms to determine the residual stress profile across welds of
  age-hardenable aluminum alloys, Appl. Soft Comput. 40 (2016) 429--438.
\newblock \href {http://dx.doi.org/10.1016/j.asoc.2015.11.004}
  {\path{doi:10.1016/j.asoc.2015.11.004}}.

\bibitem{Gong15models}
Y.~Gong, W.~Chen, Z.~Zhan, J.~Zhang, Y.~Li, Q.~Zhang, J.~Li, Distributed
  evolutionary algorithms and their models: {A} survey of the state-of-the-art,
  Appl. Soft Comput. 34 (2015) 286--300.
\newblock \href {http://dx.doi.org/10.1016/j.asoc.2015.04.061}
  {\path{doi:10.1016/j.asoc.2015.04.061}}.

\bibitem{Tonda12cooperative}
A.~P. Tonda, E.~Lutton, G.~Squillero, A benchmark for cooperative coevolution,
  Memetic Computing 4~(4) (2012) 263--277.
\newblock \href {http://dx.doi.org/10.1007/s12293-012-0095-x}
  {\path{doi:10.1007/s12293-012-0095-x}}.

\bibitem{Kimovski15Parallel}
D.~Kimovski, J.~Ortega, A.~Ortiz, R.~Ba{\~{n}}os, Parallel alternatives for
  evolutionary multi-objective optimization in unsupervised feature selection,
  Expert Syst. Appl. 42~(9) (2015) 4239--4252.
\newblock \href {http://dx.doi.org/10.1016/j.eswa.2015.01.061}
  {\path{doi:10.1016/j.eswa.2015.01.061}}.

\bibitem{Dorronsoro13superlinear}
B.~Dorronsoro, G.~Danoy, A.~J. Nebro, P.~Bouvry, Achieving super-linear
  performance in parallel multi-objective evolutionary algorithms by means of
  cooperative coevolution, Computers {\&} {OR} 40~(6) (2013) 1552--1563.
\newblock \href {http://dx.doi.org/10.1016/j.cor.2011.11.014}
  {\path{doi:10.1016/j.cor.2011.11.014}}.

\bibitem{Garcia16hpmoon}
P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~Ortega, J.~Gonz{\'{a}}lez, P.~A. Castillo,
  J.~J. Merelo, Addressing high dimensional multi-objective optimization
  problems by coevolutionary islands with overlapping search spaces, in:
  G.~Squillero, P.~Burelli (Eds.), Applications of Evolutionary Computation -
  19th European Conference, EvoApplications 2016, Porto, Portugal, March 30 -
  April 1, 2016, Proceedings, Part {II}, Vol. 9598 of Lecture Notes in Computer
  Science, Springer, 2016, pp. 107--117.

\bibitem{Deb00NSGAII}
K.~Deb, S.~Agrawal, A.~Pratap, T.~Meyarivan, A fast elitist non-dominated
  sorting genetic algorithm for multi-objective optimisation: {NSGA-II}, in:
  M.~Schoenauer, K.~Deb, G.~Rudolph, X.~Yao, E.~Lutton, J.~J.~M. Guerv{\'{o}}s,
  H.~Schwefel (Eds.), Parallel Problem Solving from Nature - {PPSN} VI, 6th
  International Conference, Paris, France, September 18-20, 2000, Proceedings,
  Vol. 1917 of Lecture Notes in Computer Science, Springer, 2000, pp. 849--858.

\bibitem{DBLP:series/ncs/EibenS15}
A.~E. Eiben, J.~E. Smith, Introduction to Evolutionary Computing, Natural
  Computing Series, Springer, 2015.
\newblock \href {http://dx.doi.org/10.1007/978-3-662-44874-8}
  {\path{doi:10.1007/978-3-662-44874-8}}.

\bibitem{DeJong2006}
K.~A. De~Jong, Evolutionary computation: a unified approach, MIT press, 2006.

\bibitem{Mora13paretobased}
A.~M. Mora, P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~J.~M. Guerv{\'{o}}s, P.~A.
  Castillo, Pareto-based multi-colony multi-objective ant colony optimization
  algorithms: an island model proposal, Soft Comput. 17~(7) (2013) 1175--1207.
\newblock \href {http://dx.doi.org/10.1007/s00500-013-0993-y}
  {\path{doi:10.1007/s00500-013-0993-y}}.

\bibitem{Talbi08Parallel}
E.~Talbi, S.~Mostaghim, T.~Okabe, H.~Ishibuchi, G.~Rudolph, C.~A.~C. Coello,
  Parallel approaches for multiobjective optimization, in: J.~Branke, K.~Deb,
  K.~Miettinen, R.~Slowinski (Eds.), Multiobjective Optimization, Interactive
  and Evolutionary Approaches [outcome of Dagstuhl seminars]., Vol. 5252 of
  Lecture Notes in Computer Science, Springer, 2008, pp. 349--372.

\bibitem{Durillo08masterslave}
A.~J. Nebro, J.~J. Durillo, A study of the parallelization of the
  multi-objective metaheuristic {MOEA/D}, in: C.~Blum, R.~Battiti (Eds.),
  Learning and Intelligent Optimization, 4th International Conference, {LION}
  4, Venice, Italy, January 18-22, 2010. Selected Papers, Vol. 6073 of Lecture
  Notes in Computer Science, Springer, 2010, pp. 303--317.
\newblock \href {http://dx.doi.org/10.1007/978-3-642-13800-3}
  {\path{doi:10.1007/978-3-642-13800-3}}.

\bibitem{Hiroyasu07discussion}
T.~Hiroyasu, K.~Yoshii, M.~Miki, Discussion of parallel model of
  multi-objective genetic algorithms on heterogeneous computational resources,
  in: H.~Lipson (Ed.), Genetic and Evolutionary Computation Conference, {GECCO}
  2007, Proceedings, London, England, UK, July 7-11, 2007, {ACM}, 2007, p. 904.

\bibitem{Deb03distributed}
K.~Deb, P.~Zope, A.~Jain, Distributed computing of pareto-optimal solutions
  with evolutionary algorithms, in: C.~M. Fonseca, P.~J. Fleming, E.~Zitzler,
  K.~Deb, L.~Thiele (Eds.), Evolutionary Multi-Criterion Optimization, Second
  International Conference, {EMO} 2003, Faro, Portugal, April 8-11, 2003,
  Proceedings, Vol. 2632 of Lecture Notes in Computer Science, Springer, 2003,
  pp. 534--549.

\bibitem{Xiao03specialized}
N.~Xiao, M.~P. Armstrong, A specialized island model and its application in
  multiobjective optimization, in: E.~Cant{\'{u}}{-}Paz, J.~A. Foster, K.~Deb,
  L.~Davis, R.~Roy, U.~O'Reilly, H.~Beyer, R.~K. Standish, G.~Kendall, S.~W.
  Wilson, M.~Harman, J.~Wegener, D.~Dasgupta, M.~A. Potter, A.~C. Schultz,
  K.~A. Dowsland, N.~Jonoska, J.~F. Miller (Eds.), Genetic and Evolutionary
  Computation - {GECCO} 2003, Genetic and Evolutionary Computation Conference,
  Chicago, IL, USA, July 12-16, 2003. Proceedings, Part {II}, Vol. 2724 of
  Lecture Notes in Computer Science, Springer, 2003, pp. 1530--1540.

\bibitem{Wang09parallel}
W.~Zhi-xin, G.~Ju, A parallel genetic algorithm in multi-objective
  optimization, in: Control and Decision Conference, 2009. CCDC '09. Chinese,
  2009, pp. 3497--3501.
\newblock \href {http://dx.doi.org/10.1109/CCDC.2009.5192490}
  {\path{doi:10.1109/CCDC.2009.5192490}}.

\bibitem{Martens13asynchronous}
M.~M{\"{a}}rtens, D.~Izzo, The asynchronous island model and {NSGA-II:} study
  of a new migration operator and its performance, in: C.~Blum, E.~Alba (Eds.),
  Genetic and Evolutionary Computation Conference, {GECCO} '13, Amsterdam, The
  Netherlands, July 6-10, 2013, {ACM}, 2013, pp. 1173--1180.

\bibitem{cheng2015adaptive}
R.~Cheng, Y.~Jin, K.~Narukawa, Adaptive reference vector generation for inverse
  model based evolutionary multiobjective optimization with degenerate and
  disconnected pareto fronts, in: Evolutionary Multi-Criterion Optimization,
  Springer International Publishing, 2015, pp. 127--140.

\bibitem{zdt2000a}
E.~Zitzler, K.~Deb, L.~Thiele, {Comparison of Multiobjective Evolutionary
  Algorithms: Empirical Results}, Evolutionary Computation 8~(2) (2000)
  173--195.

\bibitem{ECJ}
S.~Luke, et~al., {ECJ: A Java-based Evolutionary Computation and Genetic
  Programming Research System}, available at
  \url{http://www.cs.umd.edu/projects/plus/ec/ecj} (2009).

\end{thebibliography}

>>>>

In this paper we analyse several coevolutionary algorithms we have implemented by using a parallel multi-objective baseline algorithm (B) as a framework. Our proposed methods are based in NSGA-II, as almost all the previous works discussed before \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. Therefore, we have used a basic distributed NSGA-II algorithm without overlapping sections as the baseline (B). The population is distributed among $P$ islands. After a fixed number of generations, one individual in a given island is migrated to another random island, thus avoiding to synchronize the global Pareto Front (PF) every certain number of generations as other methods described in Section 2 do. At the end of the run, the Pareto Fronts of all islands are aggregated into a new one, and the quality measures are evaluated.
Different coevolutionary alternatives can be devised to evolve the subpopulations according to the decision space to be explored by each islands. Here we will consider three methods in which each island only performs crossover and mutation in specific sections of the individuals.

@@

Also, more distributed implementations in several systems (such as a
GPUs or heterogeneous clusters) with different amounts of
islands/processors, will be used to perform a scalability study of the
different methods, being the transmission time between islands a
relevant issue to address. Other MOEA algorithms available in the literature, such as SPEA or MOEA/D will be compared. Finally, new benchmarks and real problems
will also be  used to validate this approach.

@@

\bibliographystyle{elsarticle-num}
\bibliography{hpmoon-coor}
